Combining global tree cover loss data with historical national forest cover maps to look at six decades of deforestation and forest fragmentation in Madagascar

### 2018-03-14 manuscript/manuscript.Rnw
Update cover letter

Consistent with \citet{Harper2007}, we did not consider potential
forest regrowth in Madagascar (although \citet{Hansen2013} provided a
tree cover gains layer for the period 2001-2013) for several
reasons. First, the tree gain layer of \citet{Hansen2013} includes and
catches more easily tree plantations than natural forest regrowth
\citep{Tropek2014}. Second, there is little evidence of natural forest
regeneration in Madagascar \citep{Grouzis2001, Harper2007}. This can
be explained by several ecological processes following burning
practice such as soil erosion \citep{Grinand2017} and reduced seed
bank due to fire and soil loss \citep{Grouzis2001}. Moreover, in areas
where forest regeneration is ecologically possible, young forest
regrowth are more easily re-burnt for agriculture and pasture. Third,
young secondary forests provide more limited ecosystem services
compared to old-growth natural forests in terms of biodiversity and
carbon storage.

>>>>

Consistent with \citet{Harper2007}, we did not consider potential
forest regrowth in Madagascar (although \citet{Hansen2013} provided a
tree cover gains layer for the period 2001-2013) for several
reasons. First, the tree gain layer of \citet{Hansen2013} includes and
catches more easily tree plantations than natural forest regrowth
\citep{Tropek2014}. Second, there is little evidence of natural forest
regeneration in Madagascar \citep{Grouzis2001, Harper2007}. This can
be explained by several ecological processes following burning
practice such as soil erosion \citep{Grinand2017} and reduced seed
bank due to fire and soil loss \citep{Grouzis2001}. Moreover, in areas
where forest regeneration is ecologically possible, young forest
regrowth are more easily re-burnt for agriculture and pasture. Third,
young secondary forests provide more limited ecosystem services
compared to old-growth natural forests in terms of biodiversity and
carbon storage \citep{Martin2013}.
